---
title: "Module Gallery"
execute:
  echo: false
format:
  html:
    toc: true
---


## General DaVinci packages

### Module Manager by [{dv.manager}](https://boehringer-ingelheim.github.io/dv.manager/){target="_blank"}
The Module Manager is the heart of each DaVinci app. It is designed to act as container for the DaVinci modules and provide the necessary infrastructure for their operation. Additionally, {dv.manager} equips the resulting DaVinci app with various functionalities, like displaying the meta information of the data, jumping between modules, switching between different trials, or showing a custom start-up message.

### Data loader by [{dv.loader}](https://boehringer-ingelheim.github.io/dv.loader/){target="_blank"}
Besides the Module Manager, DaVinci provides another handy utility package called {dv.loader}. It facilitates data loading from either a local or remote source, such as a network file storage folder. Once the requested data is loaded, it can be passed through customized preprocessing routines and transferred to the Module Manager for display in the DaVinci app.




```{r results='asis'}
source("carousel/carousel.R")
include_images <- function(module_name) {
  folder <- file.path("images/modules", module_name)
  paths <- sort(Sys.glob(paste0(folder, "/*.png")))

  gallery_id <- paste0(module_name, "-gallery")

  if(length(paths) == 1){
    cat(paste0("![](", paths, "){width=80% fig-align='center' .lightbox group='", gallery_id, "'}"))
  } else {
    desc <- list()
    for (path in paths) desc[[length(desc)+1]] <- list(image = path, link = path)
    carousel(gallery_id, 5000, desc)
  }
}

module_template_description_pre <- r"----(  
### %s by [{%s}](%s){target='_blank'} 
  
::: columns
::: {.column width="40%%"}
)----"

module_template_description_post <- r"----(  
:::
::: {.column width="60%%"}
%s
:::
:::
)----"

describe_module <- function(name, package_name, url, image_folder, description) {
  cat(sprintf(module_template_description_pre, name, package_name, url))
  cat(knitr::raw_html(toString((include_images(image_folder)))))
  cat(sprintf(module_template_description_post, description))
}
```

## DaVinci modules
```{r, results='asis'} 
describe_module(
  'Bookmark manager', 'dv.bookman', 'https://boehringer-ingelheim.github.io/dv.bookman/', 'bookmark_manager',
  'This module lists all server-side bookmarks of a shiny application, allows to describe them and feature the most relevant ones.'
)
describe_module(
  'Boxplot', 'dv.explorer.parameter', 'https://boehringer-ingelheim.github.io/dv.explorer.parameter/articles/boxplot.html', 'boxplot',
  'The boxplot module allows visualizing parameter data from ADaM basic data structure as boxplots. Data can be displayed with different levels of grouping, listings with single subject data and the possibility of examining patient details other modules (e.g. Patient Profile). It also includes some statistical testing comparing the distribution of different groups.'
)
describe_module(
  'Clinical timelines', 'dv.clinlines', 'https://boehringer-ingelheim.github.io/dv.clinlines/', 'clinical_timelines',
  'The Clinical Timelines module allows to display subject level data over time to present dates and/or time intervals of trial events, like adverse events, concomitant medications, randomization dates, and more.'
)
describe_module(
  'Correlation heatmap', 'dv.explorer.parameter', 'https://boehringer-ingelheim.github.io/dv.explorer.parameter/articles/correlation_heatmap.html', 'correlation_heatmap',
  'The correlation heatmap module allows examining the correlation of several parameters using a correlation heatmap with different statistical measures.'
)
describe_module(
  'eDISH', 'dv.edish', 'https://boehringer-ingelheim.github.io/dv.edish/', 'edish',
  'The eDISH module is meant to support the assessment of drug-induced liver injury by means of the (modified) evaluation of Drug-Induced Serious Hepatotoxicity plot.'
)
describe_module(
  'Hierarchical count table', 'dv.tables', 'https://boehringer-ingelheim.github.io/dv.tables/articles/hierarchical_count_table.html', 'hierarchical_count',
  'The hierarchical count table module enables the visualization of hierarchical tables, displaying event counts at each level for a clear and structured overview.'
)
describe_module(
  'Forest plot', 'dv.explorer.parameter', 'https://boehringer-ingelheim.github.io/dv.explorer.parameter/articles/forest.html', 'forestplot',
  'The forest plot module allows examining the correlation of several parameters with a continuous variable in the form of a forest plot. Several correlation measures and groupings are available.'
)
describe_module(
  'Line plot', 'dv.explorer.parameter', 'https://boehringer-ingelheim.github.io/dv.explorer.parameter/articles/lineplot_main_article.html', 'lineplot',
  'The lineplot module allows examining the evolution of parameter values using lineplots with different levels of grouping and aggregation measures.'
)
describe_module(
  'Listings', 'dv.listings', 'https://boehringer-ingelheim.github.io/dv.listings/', 'listings',
  'The listings module displays arbitrary datasets as listings. Users can select the dataset to be shown, and specify which columns of the dataset should be displayed as well as their order. The displayed columns can be sorted and filtered. Moreover, the table can be filtered to show only entries containing a keyword entered by the user. The module is not limited to usage of one data source, most notably, it can handle data from ADaM or SDTM.'
)
describe_module(
  'Patient profile', 'dv.papo', 'https://boehringer-ingelheim.github.io/dv.papo/', 'patient_profile',
  'The Patient Profile module allows to display subject level information and subject related data listings as well as plots for adverse events, concomitant medications, lab values, and vital signs over time.'
)
describe_module(
  'ROC', 'dv.explorer.parameter', 'https://boehringer-ingelheim.github.io/dv.explorer.parameter/articles/roc.html', 'roc',
  'The ROC module makes it possible to visualize a set of ROC related charts, or tables, and compare independent ROC curves for different continuous parameters with respect to a single binary endpoint. This allows a user to evaluate how predictive is a continuous parameter of binary endpoint.'
)
describe_module(
  'Scatter plot', 'dv.explorer.parameter', 'https://boehringer-ingelheim.github.io/dv.explorer.parameter/articles/scatterplot.html', 'scatterplot',
  'The scatterplot module makes it possible to visualize a scatterplot of two biomarkers with different levels of grouping.'
)
describe_module(
  'Scatter plot matrix', 'dv.explorer.parameter', 'https://boehringer-ingelheim.github.io/dv.explorer.parameter/articles/scatterplotmatrix.html', 'scatterplot_matrix',
  'The scatter module allows examining the correlation of several parameters using a scatterplot matrix with different levels of grouping.'
)
describe_module(
  'Spider plot', 'dv.spiderplot', 'https://boehringer-ingelheim.github.io/dv.spiderplot/', 'spiderplot',
  'The Spiderplot module is designed for visualizing individual patient trajectories over time in clinical trials, particularly valuable for oncology efficacy analysis. This module creates spider plots that display patient-level response data, showing changes in tumor size or other clinical measurements across multiple visits.'
)
describe_module(
  'Swimmerplot', 'dv.swimmerplot', 'https://boehringer-ingelheim.github.io/dv.swimmerplot/', 'swimmerplot',
  'The Swimmerplot module enables users to create interactive swimmer plots for clinical trial data. Each patient is displayed as a horizontal swim lane showing their treatment timeline, with arrows indicating ongoing treatments and optional markers for clinical responses like tumor shrinkage or disease progression.'
)
describe_module(
  'Tplyr table', 'dv.tables', 'https://boehringer-ingelheim.github.io/dv.tables/articles/Tplyr_tables.html', 'tplyr_table',
  'The Tplyr table module enables interactive visualization of summary tables created with {Tplyr} within DaVinci apps. It acts as a wrapper that not only displays these tables but also provides traceability by linking each result cell back to its source listing using {dv.listings}. The module supports multiple Tplyr tables and standalone listings under one tab via a drop-down selector, making it easier for app creators to build flexible, auditable, and user-friendly clinical data review apps.'
)
describe_module(
  'Waterfall plus heatmap', 'dv.explorer.parameter', 'https://boehringer-ingelheim.github.io/dv.explorer.parameter/articles/wfphm.html', 'waterfall_plus_heatmap',
  'The Waterfall plus heatmap module package includes a waterfall plot and aligned categorical continuous and parameter heatmaps.'
)
```
## Other useful packages

### DaVinci's Teal wrapper package [{dv.teal}](https://boehringer-ingelheim.github.io/dv.teal/){target="_blank"}
The dv.teal package provides a wrapper function to include Teal modules within the DaVinci framework.

